The prime of their life - the halflife of acting talent

### 2017-08-31 01_actor_careers/05_report.Rmd
Many updates

> insert an image

@@

volume_chart = 
  highchart() %>%
  hc_add_theme(tmbish) %>%
  hc_chart(height = 300, spacingRight = 100) %>%
  hc_xAxis(categories = rating_volumes$age_at_production, opposite = TRUE) %>%
  hc_yAxis(
    title = list(text = "Total Films in Dataset"),
    labels = list(formatter = JS("function(){return(-1 * this.value)}"))    
    ) %>%
  hc_title(text = "") %>%
  hc_add_series(
    name = "Volumes",
    type = "area",
    data = rating_volumes$films,
    marker = list(enabled = FALSE)
  ) %>% 
  hc_legend(enabled = FALSE)

@@

@@

  highchart() %>%
    hc_add_theme(tmbish) %>%
    hc_chart(
      animation = list(duration = 2000)
    ) %>%
    hc_xAxis(
      categories = actordata$age_bucket,
      title = list(text = "Age at Production")
    ) %>%
    hc_yAxis(labels = list(formatter = JS("function(){return(this.value*100 + '%')}"))) %>%
    hc_title(text = actor) %>%
    hc_add_series(
      name = "Performance Index",
      type = "spline",
      data = actordata$index
    ) %>%
    hc_legend(enabled = FALSE)

>>>>

<br>

![Nah but actually The Intern was ok.](deniro.jpg)

<br>

@@

volume_chart = 
  highchart() %>%
  hc_add_theme(tmbish) %>%
  hc_chart(height = 300, spacingRight = 125) %>%
  hc_xAxis(categories = rating_volumes$age_at_production, opposite = TRUE) %>%
  hc_yAxis(
    title = list(text = "Total Films in Dataset"),
    labels = list(formatter = JS("function(){return(-1 * this.value)}"))    
    ) %>%
  hc_title(text = "") %>%
  hc_add_series(
    name = "Volumes",
    type = "area",
    data = rating_volumes$films,
    marker = list(enabled = FALSE)
  ) %>% 
  hc_legend(enabled = FALSE)

@@

<style>

.finding {
  background-color:#FF6A5C;
  height: 100px;
  color: #FFF;
  display: flex;
  padding-top: 10px;
  padding-bottom: 10px;
  border-radius: 25px;
  align-items: center;
  text-align:center;

.finding .sidebar {
  width: 20%;
  font-weight: bold;
  font-size: 14pt;
}

.finding .body {
  width: 80%
}

.finding img {
  display : block;
  margin : auto;
}

</style>

<br>

<div class="finding">

  <div class="sidebar"><img src="lightbulb.png"><span> Finding!</span></div>

  <div class="body"> <span> So based on this 10 film sample Denzel had a solid 40s where his films (of the likes Hurricane and Courage Under Fire) average a rotten tomatoes rating about 20% above his career average </span> </div>

</div>

<br>

@@

  highchart() %>%
    hc_add_theme(tmbish) %>%
    hc_chart(
      animation = list(duration = 2000), shadow = FALSE
    ) %>%
    hc_xAxis(
      categories = actordata$age_bucket,
      title = list(text = "Age at Production")
    ) %>%
    hc_yAxis(labels = list(formatter = JS("function(){return(this.value*100 + '%')}"))) %>%
    hc_title(text = actor) %>%
    hc_add_series(
      name = "Performance Index",
      type = "spline",
      data = actordata$index
    ) %>%
    hc_legend(enabled = FALSE)
